---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
library(prob)
```

# Question 1

## Load, clean and explore data

```{r}
customer_data <- read_csv("data/20190928-items.csv") %>% 
  clean_names()

customer_data %>% 
  glimpse()

customer_data %>% 
  head(5)

dim(customer_data)
  
```

# Question 2

## Find the brand with the highest numbers of phones in the dataset.

```{r}

customer_data %>% 
  group_by(brand) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

```
_Solution_

Samsung is most popular brand of phone with 397 reviews left from one.

# Question 3

## For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

```{r}

samsung_stats <- customer_data %>% 
  dplyr::filter(brand == "Samsung") %>% 
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )

customer_data %>% 
  dplyr::filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "grey40", bins = 30) +
  stat_function(
    fun = dnorm, args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd),
    col = "tomato"
  )

```

_Solution_

The normal distribution provides an approximate model of our data, though it is
not perfect, it provides a 'loose' fit. Our data generally follows a bell curve, 
with a few extra peaks.

# Question 4

## We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

__within 1 sd ~ 68% expected__

```{r}

samsung_scaled <- customer_data %>%
  dplyr::filter(brand == "Samsung") %>% 
  mutate(z_rating = scale(rating))

count <- samsung_scaled %>% 
  dplyr::filter(between(z_rating, left = -1, right = 1)) %>% 
  nrow()

(count / nrow(samsung_scaled))*100
```

_Solution_

79.3% of our data is within 1 sd of the sample mean. This is greater than the 
68% we would expect if it followed a normal distribution. 

__within 2 sd ~ 95% expected__

```{r}
count <- samsung_scaled %>% 
  dplyr::filter(between(z_rating, left = -2, right = 2)) %>% 
  nrow()

(count / nrow(samsung_scaled))*100
```

_Solution_

91.9% of our data lies within 2 sd of our sample mean, which falls narrowly
short of our benchmark of 95% we would expect if it followed a normal 
distribution.

__within 3 sd ~ 99.7% expected__

```{r}
count <- samsung_scaled %>% 
  dplyr::filter(between(z_rating, left = -3, right = 3)) %>% 
  nrow()

(count / nrow(samsung_scaled))*100
```

_Solution_

98.0% of our data lies within 3 sd, again, narrowly falling short of the 99.7%
we would expect to lie within 3 sd if it were to follow a normal distribution.

__Overall comments on the distribution__

After overlaying a fitted normal distribution onto our earlier probability
density plot, it was apparent that our data 'loosely' followed a normal
distribution, but not with 100% confidence (much like all statistics). The above
calculations prove this point empirically, with us only managing to satisy the
68% portion of the empirical rule and falling slightly short on the 95% & 99.7%.