---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)


## Question 1

Load in the dataset and have a look at it. What are the dimensions, variable types, variable names, etc.?
  
```{r}
## load data set
drinks_content <- read_csv("data/drinks_content.csv")

drinks_content

## calculate dimensions
dim(drinks_content)

## list variable types
str(drinks_content)

## list variable names
names(drinks_content)

```

Dimensions are 242 rows x 18 columns

## Question 2

Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.

```{r}

## Select desired columns
select(drinks_content, "Beverage_category", "Beverage", "Beverage_prep", "Calories") %>% 
  filter(is.na(Calories) == FALSE)
```
## Question 3

Create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract 135 from the calories to see which drink have more or less than 10 cups of sugar).


```{r}

mutate(drinks_content, calorie_diff = Calories - 135, .before = 1)
```

## Question 4.

Summarise the mean number of calories in each beverage_category. Which 3 category of drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.

```{r}

drinks_content %>% 
  group_by(Beverage_category) %>% 
  summarise(mean_calories = mean(Calories))


```

## Summary of findings

The three categories with the most on average, in descending order are; 
- Smoothies (282.2222 Cals)
- Frappuccino® Blended Coffee	(276.9444 Cals)
- Signature Espresso Drinks (250 Cals)

The three categories with the least average calories, in ascending order are;
- Coffee (4.25 Cals)
- Shaken Iced Beverages (114.4444 Cals)
- Classic Espresso Drinks (140.1724 Cals)


## Question 5.

Let’s look at this a different way. What is the average number of calories in each Beverage_prep type?

```{r}

drinks_content %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_calories = mean(Calories))

```

## Question 6.

Which Beverage_prep type contains more than the average calories of all drinks?
Hint
: to answer this, you’ll have to first figure out what the average calories across all drinks are, and then use that as a filter for the grouped Beverage_prep data.

```{r}
total_mean <- pull(drinks_content, Calories)
mean(total_mean)

drinks_content %>% 
  group_by(Beverage_prep) %>% 
  filter(Calories > mean(total_mean))
  

```

Question 7.

Which is the best type of coffee drink (and by ‘drink’ we mean the combination of Beverage_category, Beverage and Beverage_prep) to get if you’re worried about consuming too many calories?

