---
title: "R Notebook"
output: html_notebook
---

# Question 1.

## Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
library(tidyverse)
library(scales)
backpack_data <- CodeClanData::backpack

glimpse(backpack_data)
dim(backpack_data)
names(backpack_data)
backpack_data %>% 
  head(1)
```

# Question 2.

## What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}

ggplot(backpack_data) +
  aes(x = backpack_weight) +
  geom_bar(fill= "pink", colour = "grey40") +
  labs(title = "Distribution of Backpack Weights",
       x = "Backpack Weight (kgs)",
       y = "Frequency")+
  theme_bw()

```

__Interpretation__

From this bar chart we can view the distribution of backpack weights in our data
set. It appears that most of our backpacks are clustered between 5-15kg. The
plot also shows that the data is skewed to the right, with a few outliers
creating a right tail. We could say that this data is not normal, but instead
positively skewed.

# Question 3.

## Are there differences in backpack weight between sex?

```{r}
ggplot(backpack_data) +
  aes(x = backpack_weight, fill = sex) +
  geom_bar() +
  labs(title = "Gender Proportion in Backpacks",
       x = "Backpack Weight (kgs)",
       y = "Frequency",
       fill = "Gender")
```

__Interpretation__

From this plot we can determine that there appears to be a great number of
females wearing backpacks than males. We could also say that it appears that
females tend to wear lighter backpacks. While most males seem to wear backpacks
between 5-15kg, there are more males wearing backpacks greater than 15kg than
females.

# Question 4.

## What is the relationship between body weight and backpack weight?

```{r}

ggplot(backpack_data) +
  aes(x = backpack_weight, y = body_weight)+
  geom_point(colour = "seagreen") +
  labs(title = "Relationship Between Backpack Weight & Body Weight",
       x = "Backpack Weight (kgs)",
       y = "Body Weight (kgs)")+
  theme_bw()

```

__Interpretation__

Using this scatter plot we can see that there does appear to be a relationship
between backpack weight and body weight. It appears that that lighter a 
backpack weighs, the lighter the body weight of the person wearing it is. We
can see this due to the way the points cluster in the bottom left of the plot.

# Question 5.

## Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}

ggplot(backpack_data) +
  aes(x = backpack_weight, y = body_weight, colour = sex)+
  geom_point() +
  labs(title = "Relationship Between Backpack Weight & Body Weight by Gender",
       x = "Backpack Weight (kgs)",
       y = "Body Weight (kgs)",
       colour = "Gender")+
  theme_bw()


```

__Interpretation__

Yes, the relationship between backpack weight and body weight does seem to 
differ between gender. We can see that the orange points for females are 
clustered in a tighter group towards the bottom left corner. This shows that
the females with lower body weight tend to wear lighter backpacks. In contrast
for the men, we can see the teal points still show some correlation between
backpack weight and body weight, however, are more spread than the points of
female backpack wearers. I would guess that the correlation is stronger for
female wearers than that of men. (eg correlation coefficient for female > men)

# Question 6.

## What proportion of students report back pain?

```{r}

backpack_data %>%
  group_by(back_problems) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ggplot(backpack_data) +
  aes(x = back_problems)+
  geom_bar(fill = "orange", colour = "blue")+
  labs(title = "Proportion of Backpain in Sample",
       y = "Percentage",
       x = "Back Problems")

```

__Interpretation__

32% of students reported having backpain. 68% reported no such pain.

# Question 7.

## Is this proportion different between men and women?

```{r}

backpack_data %>%
  group_by(back_problems, sex) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ggplot(backpack_data) +
  aes(x = back_problems, fill = sex)+
  geom_bar(colour = "grey30")+
  labs(title = "Proportion of Backpain in Sample",
       y = "Percentage",
       x = "Back Problems")+
  theme_bw()

```

__Interpretation__

In those who reported having backpain, it was females who dominated this
category with 75%, compared to men at 25%. For those who reported no such pain, 
it was closer to equal, however, males edged this category 54% to females at 46%.

# Question 8.

## Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

```{r}

backpain <- backpack_data %>% 
  filter(back_problems == 1)

ggplot(backpain) +
  aes(x = backpack_weight, y = body_weight, colour = sex) +
  geom_point()+
  facet_wrap(~sex) +
  labs(title = "Backpack Weight v Bodyweight v Gender",
       y = "Body Weight (kgs)",
       x = "Backpack Weight (kgs)",
       colour = "Gender")+
  theme_bw()

ggplot(backpack_data) +
  aes(x = backpack_weight, y = body_weight, colour = sex, group = back_problems) +
  geom_point()+
  facet_wrap(~sex) +
  labs(title = "Backpack Weight v Bodyweight v Gender",
       y = "Body Weight (kgs)",
       x = "Backpack Weight (kgs)",
       colour = "Gender")+
  theme_bw()

```

__Interpretation__

In the above plots we can see that for females in the sample, those who 
suffered from backpain were largely less than 150kgs and wore backpacks less 
thn 15kgs. In the men who suffered from backpain, their bodyweight were all 
greater than 160kg, while backpack weight was firly evenly spread from 5kg to
20kg.

# Extension

# Question 1.

## Does reported backpain differ across the year groups? Ignore year 0 in your data.

```{r}
backpain <- backpack_data %>% 
  filter(back_problems == 1)

ggplot(backpain) +
  aes(x = year)+
  geom_bar(fill = "purple", colour = "grey20") +
  labs(title = "Reported Back Pain per Year Group",
       x = "Year Group",
       y = "Frequency")+
  theme_bw()

```

__Interpretation__

Reported backpack does differ across the year groups, with year group 3 the
clear leader in terms of number of students who reported backpain with 12. The
next most popular is the year group 4 with 8 cases. Years 1, 2 and 5 are closer
together.

# Question 2.

## Is there a difference between how heavy the bags those in different years carry?

```{r}
extra_heavy <- backpain %>% 
  group_by(year, backpack_weight)

ggplot(extra_heavy) +
  aes(x = year)+
  geom_bar() +
  labs(title = "Reported Back Pain per Year Group",
       x = "Year Group",
       y = "Frequency")+
  theme_bw()

```

