---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(corrplot)
library(factoextra)
library(broom)
```

```{r}
customers <- read_csv(here::here("data/mall_customers.csv")) %>% 
  clean_names()

customers_numeric <- customers %>% 
  select(annual_income_k, spending_score_1_100)
```

# Exploratory Data Analysis

```{r}
# plot of annual income and spending score
customers_numeric %>% 
  ggplot(aes(x = annual_income_k, y = spending_score_1_100)) +
  geom_point()
```

__Interpretation__

Scatter plot appears to show data would be appropriate to cluster, potentially
5 distinct clusters?

# K-means clustering

```{r}
clustered_customers <- kmeans(customers_numeric,
                        centers = 8,
                        nstart = 25)

clustered_customers

glance(clustered_customers)

```

```{r}
fviz_nbclust(customers_numeric,
             kmeans,
             method = "wss",
             nstart = 25)
```
__Interpretation__

Shows the decrease of within sum of squares as we increase the number of
clusters. We can see there is diminishing returns as we hit 5-7 clusters.

```{r}
# plot clusters
fviz_cluster(clustered_customers, customers_numeric,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800", "red", "blue",
                         "grey10", "orange", "grey40"), 
             geom = "point",
             ellipse.type = "convex", 
             ggtheme = theme_bw()
             )
```
__Interpretation__

This plot shows the points and how they have been clustered. It actually
gives me reason to believe clustering is not the best idea for this data due to
the following observations:

* We have uneven sized clusters, some > 40, some < 15.
* Appears to give more weight to larger clusters, smaller clusters have a 
greater within ss.

We can also start to label the clusters based on their location. The top right 
light grey star cluster is those grouped with high annual income and high 
spending score, the elites. Where as in the bottom left in orange there are
those with the lowest income and amongst the lowest spending score, the have
nots. I will name the green triangle cluster as the thrifty  bunch, ie, high
annual income and low spending score.

```{r}
# plot silhouette coefficient
fviz_nbclust(customers_numeric,
             kmeans,
             method = "silhouette",
             nstart = 25)
```
__Interpretation__

This silhouette coefficient shows us the optimal number of clusters appears to
be 5.
