---
title: "R Notebook"
output: html_notebook
---
# load relevant libraries

```{r}
library(tidyverse)
library(janitor)
library(ggplot2)
library(corrr)
```

# read in data

```{r}
books_data <- read_csv("data/books.csv")
```

# Preliminary data exploration

Data has 11123 rows and 13 columns. It is a list of books from goodreads that
includes; their average rating out of 5, the number of ratings, the author, to
name a few objects in the data.

There also are no NA values to concern us.

```{r}

glimpse(books_data)

head(books_data, 5)

tail(books_data, 5)

dim(books_data)

sum(is.na(books_data))

```

# clean the data

Use the janitor function to move object names to lowercase and ensure
snakecase throughout. Also create a new variable, books_data_clean, this 
will avoid any confusion later on. This will be the data set analysed from here.

```{r}
books_data %>% 
  names()

books_data_clean <- books_data %>% 
  clean_names()

books_data_clean %>% 
  names()

```

# begin data wrangling

# How many distinct authors appear in this data frame?

6639 distinct authors! However, it appears that it appears some
illustrators have been included in this data set. Something we should keep
in mind when analysing by author.

```{r}

books_data_clean %>% 
  distinct(authors)

```

# Arrange the titles by ISBN as a way of indexing the data

```{r}

books_data_clean %>% 
  select(title, isbn) %>% 
  arrange(isbn)

```


# How many books have a 5 rating?

It appears that 22 books on our list were given a perfect 5 rating!

```{r}

five_average_rating <- books_data_clean %>%
  select(title, average_rating, publisher) %>%
  filter(average_rating == 5)

five_average_rating
  
```

# What are the 5 longest books by number of pages?

In case you feel like challenging yourself to reading the longest books!

```{r}

books_data_clean %>%
  select(title, num_pages) %>% 
  slice_max(num_pages, n = 5)

books_data_clean %>%
  select(title, num_pages) %>% 
  slice_min(num_pages, n = 5)
  
```

# Remove the 'zero page' titles

There are 76 titles with zero pages, for the purposes of this data set I feel
it appropriate to create a new subset without these titles.

I have created a new object; non_zero_books which no longer includes titles
with zero pages. This could be useful in other analysis if we wish to only
investigate books that actually contain pages.

```{r}

books_data_clean %>% 
  select(num_pages) %>% 
  summarise(sum(num_pages == 0))

non_zero_books <- books_data_clean %>% 
  select(title, num_pages) %>% 
  filter(!num_pages == 0)

non_zero_books

```



# Creating a new column that finds the difference in page length from the mean

This could be useful to determine whether or not you'd like to read the book, 
given on how many more (or fewer) pages it deviates from the mean number of
pages.

```{r}

non_zero_books %>%
  select(title, num_pages) %>% 
  mutate(diff_from_mean_pages <- num_pages - mean(num_pages))

```

# Lets view the difference by using the median instead of mean

```{r}

non_zero_books %>%
  select(title, num_pages) %>% 
  mutate(diff_from_mean_pages <- num_pages - median(num_pages))

```


# Lets compare books written with "eng" as a language code to those without

```{r}

books_data_clean %>% 
  select(language_code) %>% 
  group_by(language_code)

eng_language <- books_data_clean %>% 
  select(language_code) %>% 
  mutate(language_code = if_else(language_code == "eng", "english", "non-english")) 

eng_language

```


# Is there a correlation between the average rating and ratings count?

Using ggplot to create a scatter plot we can see there is a weak positive
correlation between the average rating and the ratings count. This could be
explianed by the fact that popular books, ie those rated numerously, would
be continually rated and favoured well.

```{r}

names(books_data_clean)
ggplot(data = books_data_clean) +
  geom_point(aes(x = average_rating, y = log(num_pages))) + 
  theme_bw()

```

# Correlation coefficient between ratings_count, average_rating and num_pages

To further explore the plot above, I decided to calculate the correlation
coefficient between the three objects. It is clear to see there is close to no
correlation between any of them. The most significant being a correlation
coefficient of 0.15 (3sf) between average_rating and num_pages.

```{r}

cor_ratings <- books_data_clean %>% 
  select(ratings_count, average_rating, num_pages)

correlate(cor_ratings)

```

