---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
```


# Question 1

## Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
rev_data <- CodeClanData::qb_revenue_breakdown

ggplot(rev_data) +
  aes(x = Year, y = Revenue, fill = Product) +
  geom_col() +
  labs(title = "Revenue sources per Year")
  

```

# Question 2

## Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).

```{r}

monthly_sales <- CodeClanData::qb_monthly_sales

kwikbit <- monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales")

ggplot(kwikbit) +
  aes(x = Date, y = Amount) +
  geom_line() +
  labs(title = "Kwikbit sales '18-19")
  
  
```

# Question 3

## Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}

without_kwikbit <- monthly_sales %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales")

ggplot(without_kwikbit)+
  aes(x = Date, y = Amount, colour = Cashflow) +
  geom_line() +
  labs(title = "Revenue v Costs 2018-19")

# fixed to remove kwikbit sales from graph
```

# Question 4

## Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}

fitness_trackers <- CodeClanData::qb_competitors

options(scipen = 999)                   # turn off scientific notation
ggplot(fitness_trackers) +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_area() +
  labs(title = "Fitness Tracker Sales by Company")

```

# Question 5

## Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}

ggplot(fitness_trackers)+
  geom_line(aes(x = Year, y = Revenue, colour = Company), alpha = 0.3) +
  geom_point(aes(x = Year, y = Revenue, colour = Company), alpha = 0.5) +
  geom_smooth(aes(x = Year, y = Revenue, colour = Company)) +
  labs(title = "Sales by Company")

```

# Question 6

## Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}

device_data <- CodeClanData::qb_device_data

device_data <- device_data %>% 
  mutate(minute_hours = ((hours*60)+mins))

ggplot(device_data) +
  geom_line(aes(x = minute_hours, y = counts, colour = device), show.legend = F) +
  facet_grid(device~id) +
  labs(title = "Our Steps v Competitors",
       x = "Minutes",
       y = "Step Count")
  
# changed from geom_point to geom_line to view trends better
```

