---
title: "weekend homework"
subtitle: "hypothesis testing"
output: html_notebook
---

# Load Packages

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

# Read in Sleep Data

```{r}
sleep <- ggplot2::msleep %>% 
  clean_names()
```

# Question 1.

## Explore the dataset and familiarise yourself with it.

```{r}
# dimensions of data 
dim(sleep)

# glimpse whole data set
glimpse(sleep)
```

# Question 2.

## Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

### Hypotheses

_Null_: There is no difference in mean sleep total and jabberwockie mean sleep.

$$H_0: \mu_{sleep\ total} - \mu_{jabberwockie\ sleep} = 0$$

_Alternative_: There is a statistically significant difference in mean sleep total
and mean jabberwockie sleep.

$$H_A: \mu_{sleep\ total} - \mu_{jabberwockie\ sleep} \ne 0$$
### Alpha level

For the purposes of this hypothesis test, _alpha = 0.05_

### Calculate observed statistic

```{r}
obs_stat <- sleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))

obs_stat
```

### Create Null Sampling Distribution

```{r}
null_dist <- sleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 0) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_dist
```

### Visualise Observed Stat on Null Sampling Distribution

```{r}
null_dist %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = obs_stat$mean_sleep_total, direction = "both")
```

_Interpretation_

Visually, it appears that there may be a statistically significant difference
in the mean sleep total for the animals in our data set and the mean sleep for
jabberwockies. This is due to the extreme right location of our observed 
statistic (red line) in relation to our normal sampling null distribution.

### Calculate p-value

```{r}
null_dist %>% 
  get_p_value(obs_stat = obs_stat, direction = "both")
```

_Outcome_

Since our p-value of 0 < 0.05 (alpha), we reject the null hypothesis that the
difference in mean sleep total and mean jabberwockie sleep is zero. It would 
appear that a more suitable assumption is that there is a statistically
significant difference in the mean sleep totals of animals v jabberwockies.

# Question 3.

## Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

### Hypotheses

H0: The mean sleep for omnivores <= mean sleep for herbivores

$$H_0: \mu_{omnivore\ sleep} <or=\ \mu_{herbivore\ sleep}$$

Ha: The mean sleep for omnivores > mean sleep for herbivores

$$H_A: \mu_{omnivore\ sleep} >\ \mu_{herbivore\ sleep}$$


### Alpha Level

For this hypothesis test alpha = 0.05

### Calculate Observed Statistic

```{r}

o


let_observed_stat <- let_prices %>% 
  specify(price~location) %>% 
  calculate(stat = "diff in means", order = c("florence", "corfu"))
```


